---
title: "N736 Homework 01"
author: "Gaea Daniel"
date: "September 6, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load packages
library(splines)
library(RcmdrMisc)
library(car)
library(sandwich)
library(effects)
library(Rcmdr)
```

## N736 Homework 01 - Due Sept 6, 2017

1. Using your statistical software of choice, read in the dataset "Dataset_02" from the `*.CSV`, `*.XLS` or `*.XLSX` format.

```{r}
#View original data
View(Dataset_02)
#Import data after edit (q2 input shifted up by one cell)
library(readxl)
Dataset_02_Edit <- read_excel("~/RStudio Stuff/N736Testdataset/Dataset_02_Edit.xlsx")
View(Dataset_02_Edit)
```

2. Create an analysis report that explains **`every step you did`** - including anything you did manually. Ideally, everything you do to the dataset for fixing the errors or identifying the issues you spot in the data should be done using CODE (aka SYNTAX) so that someone else can take your code and reproduce your results. _[Remember, that "someone else" might be you in a few weeks when you've forgotten what you did earlier...]_

Corrections to be made:
GenderSTR formatting
q4 - outlier 40
q1 - outlier 11
q2-q5 - contains 9's
GenderCoded - missing values
WeightPRE - outliers 68, 60 (typo or lbs vs kg)
Height - 2.6 (amputee)
Age - outlier 99
9's could indicate missing, refused to anser, N/A, I don't know
SubjectID's not consecutive
q2 - shifted down by 1 cell
q3,4,5 missing for last 3 submects (skipped items maybe on back or swithched to short form)

3. Provide comments and an explanation in your analysis report and in your code for each issue you find and fix.
4. HINT: There are 10 issues to identify or problems to fix in this dataset. One of the issues might have to be done manually, but you should still explain what you did to fix it, even if you did it manually.
5. Turn in - upload to CANVAS no later than Sept 6, 2017 11:59pm:
    (A) An analysis/data preparation report (in either `DOC` or `PDF` format) - don't forget to format your report nicely, make sure your name and date is included and
    (B) your code/syntax with your comments and commands used to reproduce your results (you can upload your code in either `*.R`, `*.sas`, `*.sps` or `*.txt` (i.e. plain text) formats)
